### 2012-08-02 Doc/VRIPHYS2012/vriphys2012.tex
proofread of section 5
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@450 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In subsections \ref{sec-roof} and \ref{sec-hemisphere} we present tests to
validate the convergence of our B\'ezier shell element. As a reference we use a
combination of two elements that are very well established in the area of
mechanical modelling. Our results are compared with the shell element composed
of Discrete Kirchoff Triangle (DKT) element \cite{Batoz1980} for bending plate
and optimal ANDES element \cite{Felippa2003} for membrane. For comparison the
results for the model of O. Comas are also presented. Subsection \ref{sec-fps}
presents evaluation of the computational complexity of our solution. Last
subsections are dedicated to presentation of application of our model.

@@

Second performed test is a hemisphere with hole subjected to two opposing
forces at the base. The geometry is described by a hemisphere with radius
$r=10$ and thickness $t=0.04$ with 18° hole at the top and the geometry is
discretized into the grid of NxN vertices per quadrant. The physical
parameters are $E = 6.825 \times 10^7$ and $\nu = 0.3$. The hemisphere is
at it's base subjected to two opposing outwards forces and two opposing
inwards forces with magnitude $P = 4$. To avoid rigid body movement we have
constrained two opposite nodes at the top of the hemisphere. The radial
displacement for one point with applied load is shown in Figure
\ref{fig-hemisphere}.

@@

\subsection{Simulation of a Birth}

\FigureW{\linewidth}{birth}
{Screenshots from the simulation of child head during birth. Full visualisation (left) and the mechanical mesh (right).}

The purpose of another simulator kkk 
- Simulation of birth ! (Try to see where the tissue' stress is the highest)

The trajectory of the baby-head during the birth is predefined. The collisions response drives the deformations of the uterus.
Mechanically, the uterus is modeled with 127 shells solved by a direct solver (LDL factorization).
Up to 60 instantaneous contact spots, simulated at 6 FPS.
The goal is to reproduce the mechanical solicitations on the anatomical structure during the birth.

@@

>>>>

In subsections \ref{sec-roof} and \ref{sec-hemisphere} we present tests to
validate the convergence of our B\'ezier shell element. As a reference we use a
combination of two elements that are very well established in the area of
mechanical modelling. Our results are compared with the shell element composed
of Discrete Kirchoff Triangle (DKT) element \cite{Batoz1980} for bending plate
and optimal ANDES element \cite{Felippa2003} for membrane. For comparison the
results for the model of O. Comas \cite{Comas2010c} are also presented. 
Subsection \ref{sec-fps}
presents evaluation of the computational complexity of our solution. Last
subsections are dedicated to presentation of application of our model.

@@

Second performed test is an hemisphere with hole subjected to two opposing
forces at the base. The geometry is described by a hemisphere with radius
$r=10$ and thickness $t=0.04$ with 18° hole at the top and the geometry is
discretized into the grid of NxN vertices per quadrant. The physical
parameters are $E = 6.825 \times 10^7$ and $\nu = 0.3$. The hemisphere is
at it's base subjected to two opposing outwards forces and two opposing
inwards forces with magnitude $P = 4$. To avoid rigid body movement we have
constrained two opposite nodes at the top of the hemisphere. The radial
displacement for one point with applied load is shown in Figure
\ref{fig-hemisphere}.

@@

\subsection{Simulation of uterus deformation during birth}

\FigureW{\linewidth}{birth}
{Screenshots from the simulation of child head during birth. Full visualization (left) and the mechanical mesh (right).}

The purpose of this simulator is to reproduce the tissue deformations that are encountered during a delivery.
The goal is to evaluate the mechanical stresses which are applied on the anatomical structures (like the uterus but also like the ligaments that sustain the uterus).

The data comes from a MRI of a 8 months pregnant woman. 
The trajectory of the baby-head during the birth was predefined with gynecologists. 
The model is limited to uterus deformations but will soon account for the vaginal tissues deformation.
The collisions response drives the deformations of the uterus.
Mechanically, the uterus is modeled with 127 shells that are solved by a direct solver (LDL factorization).
Up to 60 instantaneous contact spots need to be mapped on the shell elements. 
The simulation frame-rate is relatively low (6 FPS) due to contact response computation.

@@

In future work, we will investigate the use of more complex constitutive laws and also the use of GPU for parallel and faster compuation.
